---
title: "Dissertation Participant 3"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r setup 1, include=FALSE}
library(tidyverse)
library(rio)
library(here)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(SCVA)
library(patchwork)


theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )

brief_parent <- import(here("data", "GOZO_brief_parent.xlsx"),
               setclass = "tbl_df") 
 
brief_self <- import(here("data", "GOZO_brief_self.xlsx"),
               setclass = "tbl_df") 

class_self_1 <- import(here("data", "GOZO_class_self_1.xlsx"),
               setclass = "tbl_df") 

class_self_2 <- import(here("data", "GOZO_class_self_2.xlsx"),
               setclass = "tbl_df") 

class_parent_1 <- import(here("data", "GOZO_class_parent_1.xlsx"),
               setclass = "tbl_df") 

class_parent_2 <- import(here("data", "GOZO_class_parent_2.xlsx"),
               setclass = "tbl_df") 

pcss <- import(here("data", "GOZO_pcss.xlsx"),
               setclass = "tbl_df") 

status <- import(here("data", "GOZO_status_goal.xlsx"),
               setclass = "tbl_df") 

status_all <- import(here("data", "GOZO_status_all.xlsx"),
               setclass = "tbl_df") 

gas <- import(here("data", "GOZO_gas.xlsx"),
               setclass = "tbl_df") 

demo <- import(here("data", "GOZO_demo.xlsx"),
               setclass = "tbl_df")
```

## Demographic Information 

```{r, include=FALSE}
head(demo)

demo_tbl <- demo %>% 
  gt() %>% 
  cols_label(Sex = "Sex",
             Age = "Age",
             prev_con = "Prior Concussions",
             hx_depression = "History of Depression or Anxiety") %>% 
  cols_align(align = "center", 
             columns = vars(Sex, Age, prev_con, hx_depression)) %>% 
 tab_header(title = "Participant Demographics")

demo_tbl
```

```{r, include=TRUE}
demo_tbl
```

## Outcome Measurements 

### GAS Hierarchy - Increase weekly assignment completion 

```{r, include=FALSE}
head(gas)

gas_tbl <- gas %>% 
  reactable(columns = list(
    Level = colDef(align = "center"),
    Outcome = colDef(align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    height = 200,
    width = 500)
```

```{r, include=TRUE, fig.height=8}
gas_tbl
```

### BRIEF-2 {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
head(brief_parent)
head(brief_self)

brief_self_tidy <- brief_self %>% 
  pivot_longer(
    cols = c(`Pre Baseline Phase`, 
             `Pre Experimental Phase`,
             `Post Treatment`),
    names_to = "Assessment",
    values_to = "Response"
  )

head(brief_self_tidy)

brief_scales <- c("Global Executive Composite",
                  "Cognitive Regulation Index",
                  "Organization Scale",
                  "Task Completion Scale",
                  "Plan/Organize Scale",
                  "Working Memory Scale",
                  "Initiate Scale",
                  "Emotional Regulation Index",
                  "Emotional Control Scale",
                  "Shift Scale",
                  "Behavior Regulation Index",
                  "Self-Monitor Scale",
                  "Inhibit Scale")

brief_self_tidy$Assessment <- factor(brief_self_tidy$Assessment, 
                                     levels = c("Pre Baseline Phase",
                                                "Pre Experimental Phase",
                                                "Post Treatment"))

brief_self_plot <- ggplot(brief_self_tidy, aes(`Scale/Index`, `Response`)) +
  geom_line(aes(group = `Scale/Index`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  scale_color_OkabeIto() +
  coord_flip() +
  scale_x_discrete(limits = brief_scales) +
  scale_y_continuous(limits = c(30, 90),
                     breaks = c(30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90)) +
  geom_text_repel(aes(label = `Response`)) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "BRIEF-2 Self-Report",
       color = NULL,
       subtitle = "Scores Greater than 65 are Considered Clinically Significant")

brief_self_plot


brief_parent_tidy <- brief_parent %>% 
  pivot_longer(
    cols = c(`Pre Baseline Phase`, 
             `Pre Experimental Phase`,
             `Post Treatment`),
    names_to = "Assessment",
    values_to = "Response"
  )

brief_parent_tidy$Assessment <- factor(brief_parent_tidy$Assessment,
                                       levels = c("Pre Baseline Phase",
                                                "Pre Experimental Phase",
                                                "Post Treatment"))

brief_parent_plot <- ggplot(brief_parent_tidy, aes(`Scale/Index`, `Response`)) +
  geom_line(aes(group = `Scale/Index`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  scale_color_OkabeIto() +
  coord_flip() +
  scale_x_discrete(limits = brief_scales) +
  scale_y_continuous(limits = c(30, 90),
                     breaks = c(30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90)) +
  geom_text_repel(aes(label = `Response`)) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "BRIEF-2 Parent-Report",
       color = NULL,
       subtitle = "Scores Greater than 65 are Considered Clinically Significant")

brief_parent_plot

head(brief_parent)

brief_tbl <- function(df) {
  df %>% 
  reactable(
    columns = list(
      `Scale/Index` = colDef(align = "center"),
      `Pre Baseline Phase` = colDef(name = "Pre Baseline Phase",
                                    align = "center"),
      `Pre Experimental Phase` = colDef(name = "Pre Experimental Phase",
                                        align = "center"),
      `Post Treatment` = colDef(name = "Post Treatment",
                                align = "center")),
    pagination = FALSE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE,
    height = 600,
    width = 500)
}
  
brief_tbl(brief_self)


brief_self_2 <- brief_self %>% 
  filter(`Scale/Index` != "Initiate Scale",
         `Scale/Index` != "Organization Scale")



brief_self_2 %>% 
  reactable(
    columns = list(
      `Scale/Index` = colDef(align = "center"),
      `Pre Baseline Phase` = colDef(name = "Pre Baseline Phase",
                                    align = "center",
                                    style = function(value) {
                                      if (value >= 65) {
                                        color <- "#e00000"
                                      } else if (value < 65) {
                                        color <- "#008000"
                                      } else {
                                        color <- "#777"
                                      } 
                                       list(color = color, fontWeight = "bold")
                                    }
                                      ),
      `Pre Experimental Phase` = colDef(name = "Pre Experimental Phase",
                                        align = "center"),
      `Post Treatment` = colDef(name = "Post Treatment",
                                align = "center")),
    pagination = FALSE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE,
    height = 600,
    width = 500)

brief_color_tbl <- function(df) {
  df %>% 
  reactable(
    columns = list(
      `Scale/Index` = colDef(align = "center"),
      `Pre Baseline Phase` = colDef(name = "Pre Baseline Phase",
                                    align = "center",
                                    style = function(value) {
                                      if (value >= 65) {
                                        color <- "#e00000"
                                      } else if (value < 65) {
                                        color <- "#008000"
                                      } else {
                                        color <- "#777"
                                      } 
                                       list(color = color, fontWeight = "bold")
                                    }
                                      ),
      `Pre Experimental Phase` = colDef(name = "Pre Experimental Phase",
                                        align = "center"),
      `Post Treatment` = colDef(name = "Post Treatment",
                                align = "center")),
    pagination = FALSE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE,
    height = 600,
    width = 500)
}

brief_color_tbl(brief_self_2)
```

#### BRIEF-2 Self-Report Plot

```{r, include=TRUE, fig.height=8, fig.width=10}
brief_self_plot
```

#### BRIEF-2 Self-Report Table

```{r, include=TRUE, fig.height=8}
brief_color_tbl(brief_self_2)
```

#### BRIEF-2 Parent-Report Plot

```{r, include=TRUE, fig.height=8, fig.width=10}
brief_parent_plot
```

#### BRIEF-2 Parent-Report Table

```{r, include=TRUE, fig.height=8}
brief_color_tbl(brief_parent)
```

### CLASS {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
head(class_self_1)
head(class_self_2)
head(class_parent_1)
head(class_parent_2)

class_self_1_tidy <- class_self_1 %>% 
  pivot_longer(
    cols = c(`Pre Baseline Phase`,
             `Pre Experimental Phase`,
             `Post Treatment`),
    names_to = "Assessment",
    values_to = "Response"
  )

class_1 <- c("Easily bothered by lights/screens or noise",
             "Tiring easily during homework",
             "Tiring easily during the school day",
             "Headaches interfering with homework",
             "Headaches interfering with classwork",
             "Easily distracted during homework",
             "Easily distracted during classwork",
             "Trouble reading",
             "Trouble remembering what was studied",
             "Difficulty studying for tests or quizzes",
             "Homework taking longer",
             "In class, work taking longer",
             "Difficulty understanding new material",
             "Difficulty taking notes")

class_1_resp <- c("A lot worse",
                  "Somewhat worse",
                  "A little worse",
                  "Not worse")

class_self_1_tidy$Assessment <- factor(class_self_1_tidy$Assessment,
                                       levels = c("Pre Baseline Phase",
                                                  "Pre Experimental Phase",
                                                  "Post Treatment"))

class_self_1_plot <- ggplot(class_self_1_tidy, aes(`Question`, `Response`)) +
  geom_line(aes(group = `Question`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  scale_color_OkabeIto() +
  coord_flip() +
  scale_x_discrete(limits = class_1) +
  scale_y_discrete(limits = class_1_resp) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "CLASS Responses",
       color = NULL,
       subtitle = "Questions 1-14")

class_self_1_plot

class_self_2_tidy <- class_self_2 %>% 
  pivot_longer(
    cols = c(`Pre Baseline Phase`,
             `Pre Experimental Phase`,
             `Post Treatment`),
    names_to = "Assessment",
    values_to = "Response"
  )

class_2 <- c("Stressed out about your grades dropping",
             "More stressed out/overwhelmed with the schoolwork piling up",
             "Not having enough support at home from parents/siblings",
             "Not having enough support from teachers",
             "Not being allowed to play sports/recreation",
             "Missing time with friends and/or social activities")

class_2_resp <- c("Very stressful",
                  "Moderately stressful",
                  "A little stressful",
                  "Not stressful")

class_self_2_tidy$Assessment <- factor(class_self_2_tidy$Assessment,
                                       levels = c("Pre Baseline Phase",
                                                  "Pre Experimental Phase",
                                                  "Post Treatment"))

class_self_2_plot <- ggplot(class_self_2_tidy, aes(`Question`, `Response`)) +
  geom_line(aes(group = `Question`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  scale_color_OkabeIto() +
  coord_flip() +
  scale_x_discrete(limits = class_2) +
  scale_y_discrete(limits = class_2_resp) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "CLASS Responses",
       color = NULL,
       subtitle = "Questions 15-20")

class_self_2_plot

class_parent_1_tidy <- class_parent_1 %>% 
  pivot_longer(
    cols = c(`Pre Baseline Phase`,
             `Pre Experimental Phase`,
             `Post Treatment`),
    names_to = "Assessment",
    values_to = "Response"
  )

class_parent_1_tidy$Assessment <- factor(class_parent_1_tidy$Assessment,
                                         levels = c("Pre Baseline Phase",
                                                    "Pre Experimental Phase",
                                                    "Post Treatment"))

class_parent_1_plot <- ggplot(class_parent_1_tidy, aes(`Question`, `Response`)) +
  geom_line(aes(group = `Question`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  scale_color_OkabeIto() +
  coord_flip() +
  scale_x_discrete(limits = class_1) +
  scale_y_discrete(limits = class_1_resp) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "CLASS Responses",
       color = NULL,
       subtitle = "Questions 1-14")

class_parent_1_plot

class_parent_2_tidy <- class_parent_2 %>% 
  pivot_longer(
    cols = c(`Pre Baseline Phase`,
             `Pre Experimental Phase`,
             `Post Treatment`),
    names_to = "Assessment",
    values_to = "Response"
  )

class_parent_2_tidy$Assessment <- factor(class_parent_2_tidy$Assessment,
                                         levels = c("Pre Baseline Phase",
                                                    "Pre Experimental Phase",
                                                    "Post Treatment"))

class_parent_2_plot <- ggplot(class_parent_2_tidy, aes(`Question`, `Response`)) +
  geom_line(aes(group = `Question`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  scale_color_OkabeIto() +
  coord_flip() +
  scale_x_discrete(limits = class_2) +
  scale_y_discrete(limits = class_2_resp) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       color = NULL,
       title = "CLASS Responses",
       subtitle = "Questions 15-20")

class_parent_2_plot

head(class_parent_1)

class_self_all <- bind_rows(class_self_1, class_self_2)
class_parent_all <- bind_rows(class_parent_1, class_parent_2)

class_tbl <- function(df) {
  df %>% 
  reactable(
    columns = list(
      `Question` = colDef(align = "center"),
      `Pre Baseline Phase` = colDef(name = "Pre Baseline Phase",
                                    align = "center"),
      `Pre Experimental Phase` = colDef(name = "Pre Experimental Phase",
                                        align = "center"),
      `Post Treatment` = colDef(name = "Post Treatment",
                                align = "center")),
    pagination = FALSE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE,
    height = 600,
    width = 500)
}
```

#### CLASS Self 1 

```{r, include=TRUE, fig.height=8, fig.width=10}
class_self_1_plot
```

#### CLASS Self 2

```{r, include=TRUE, fig.height=8, fig.width=11}
class_self_2_plot
```

#### ClASS Self Table

```{r, include=TRUE, fig.height=8}
class_tbl(class_self_all)
```

#### CLASS Parent 1

```{r, include=TRUE, fig.height=8, fig.width=10}
class_parent_1_plot
```

#### CLASS parent 2

```{r, include=TRUE, fig.height=8, fig.width=11}
class_parent_2_plot
```

#### ClASS Parent Table

```{r, include=TRUE, fig.height=8}
class_tbl(class_parent_all)
```

### PCSS

```{r, include=FALSE}
head(pcss)

pcss_table <- pcss %>% 
  reactable(
    columns = list(
      Symptom = colDef(align = "center"),
      `Pre Baseline Phase` = colDef(name = "Pre Baseline Phase",
                                    align = "center"),
      `Pre Experimental Phase` = colDef(name = "Pre Experimental Phase",
                                        align = "center"),
      `Post Treatment` = colDef(name = "Post Treatment",
                                align = "center")),
    pagination = FALSE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE,
    height = 600,
    width = 500)
```

```{r pcss table, include=TRUE, fig.height=8}
pcss_table
```

## Repeated Measurements 

### Status Tracking Measurement

```{r, include=FALSE}
head(status)

#status_plot <- ggplot() +
  #geom_line(data = status, aes(x = session, y = bl)) +
  #geom_point(data = status, aes(x = session, y = bl), size = 2) +
  #geom_line(data = status, aes(x = session, y = tx)) +
  #geom_point(data = status, aes(x = session, y = tx), size = 2) +
  #scale_x_continuous(limits = c(0, 13),
                     #breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13)) +
  #scale_y_continuous(limits = c(0, 60),
                     #breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60)) +
  #theme_classic() +
  #theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  #labs(x = "Session",
       #y = "Number of Minutes",
       #title = "Number of Minutes per Class Engaged in Online Spanish Lecture") 

#status_plot

head(status_all)

status_plot_all <- ggplot(status_all, aes(session, status)) +
  geom_line() +
  geom_point(size = 2) +
  scale_x_continuous(limits = c(0, 13),
                     breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13)) +
  scale_y_continuous(limits = c(0, 100),
                     breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100),
                     labels = function(x) paste0(x, "%")) +
  theme_classic() +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  labs(x = "Session",
       y = "Percentage of Weekly Assignments Completed",
       title = "Status Tracking Goal") 

status_plot_all

```

```{r, include=TRUE}
status_plot_all
```